Supplemental Information: remote sensing riverine gas exchange and carbon efflux using SWOT observations

### 2021-02-17 supp_v1.Rmd
manuscript edits

---
title: "Supplemental Information"
author: "CB Brinkerhoff, CJ Gleason, PA Raymond, MH Harlan"
date: "`r Sys.Date()`"
csl: APA.csl
output:
  word_document: 
      reference_docx: word-styles-reference.docx
bibliography: References.bib

@@

##Text S2
In Figure S4 we show that bed roughness only exerts an influence on $k_{600}$ when rivers are incredibly steep. We do this using the 'Keulegan effective roughness height' for the channel bed, which is detailed in equation S1 below (in the form form [@dingmanAnalyticalDerivationAtastation2007b]). This model was first outlined in the 1930s by Keulegan and outlined explicitly in [@fergusonHydraulicsHydraulicGeometry1986a] and [@dingmanAnalyticalDerivationAtastation2007b] in the context of hydraulic geometry (noting that it is a more generalized form of the Manning's and Chezy's velocity~depth relations commonly used in the literature). The model arises from depth integrating the Prandl-von Karman equation for velocity in a turbulent boundary layer ($\frac{u}{u_\star}=2.5ln(\frac{30y}{k_s})$) [@[@fergusonHydraulicsHydraulicGeometry1986a]].

@@

![Figure S1 Timeseries of the biweekly CO2 data from Beaulieu et al. (2012). Sampling took place 2008-2009 in the Ohio River (upstream of Cincinnati, OH). Each point here was joined to the 11-day SWOT observations used in this study (section 5.2.4).](outputs/flux_implications/Beaulieu_timeseries.jpg)

![Figure S2 Histogram of equation 3 uncertainty terms extracted from 8,000 different Monte Carlo simulations (following that outlined in section 5.2.2). This indicates estimate uncertainty from the ai and bi parameters (and not Manning’s equation). Dashed blue line indicates the mean uncertainty (1.30 in ln-space, or ~3.67 m/day).](outputs/MonteCarlo/noMannings.jpeg)

![Figure S3. Scaling $k_{600}$ using an effective bed roughness term (see Text S2). This scaling relationship only exists for rivers with very steep slopes, here presented as greater than 0.1](outputs/k600/roughness.jpg)

>>>>

---
title: "Supplemental Information: remote sensing riverine gas exchange and carbon efflux using SWOT observations"
author: "CB Brinkerhoff, CJ Gleason, PA Raymond, MH Harlan"
date: "`r Sys.Date()`"
csl: rse_citation_style.csl
output:
  word_document: 
      reference_docx: word-styles-reference.docx
bibliography: References.bib

@@

##Text S2
In Figure S4 we show that bed roughness only exerts an influence on $k_{600}$ when rivers are incredibly steep. We do this using the 'Keulegan effective roughness height' for the channel bed, which is detailed in equation S1 below (in the form form [@dingmanAnalyticalDerivationAtastation2007b]). This model was first outlined in the 1930s by Keulegan and outlined explicitly in [@fergusonHydraulicsHydraulicGeometry1986a] and [@dingmanAnalyticalDerivationAtastation2007b] in the context of hydraulic geometry (noting that it is a more generalized form of the Manning's and Chezy's velocity~depth relations commonly used in the literature). The model arises from depth integrating the Prandl-von Karman equation for velocity in a turbulent boundary layer ($\frac{u}{u_\star}=2.5ln(\frac{30y}{k_s})$) [@fergusonHydraulicsHydraulicGeometry1986a].

@@

![Figure S1 Timeseries of the biweekly CO2 data from Beaulieu et al. (2012). Sampling took place 2008-2009 in the Ohio River (upstream of Cincinnati, OH). Each point here was joined to the 11-day SWOT observations used in this study (section 5.2.4).](outputs/FCO2/Beaulieu_timeseries.jpg)

![Figure S2. Scaling $k_{600}$ using an effective bed roughness term (see Text S2). This scaling relationship only exists for rivers with very steep slopes, here presented as greater than 0.1](outputs/k600/roughness.jpg)
